Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-23 Manuscript/manuscript.Rmd
Review

Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses. It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors for each cell line (Figure 5). Results remained consistent across the other data resolutions (Supplementary Figure 3). Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to resolution and cell line. The sets of top predictors chosen varied across resolution and cell line due to differences in the parameters provided in the TAD calling algorithm (Supplementary Table 3). For the 10 kb resolution data, the most important predictive features that were robust across cell lines were a mixture of transcription factor binding sites, chromatin states, and histone modifications including Smc3, Rad21, CTCF, and H3k9 trimethylation (Figure 6). Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 4). Results when cell lines were compared across the 100 kb resolutions were less consitent with current literature.

>>>>

Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses. It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors [??? Distance-based only?] for each cell line (Figure 5). Results remained consistent across the other data resolutions (Supplementary Figure 3). Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to resolution and cell line. The sets of top predictors chosen varied across resolution and cell line due to differences in the parameters provided in the TAD calling algorithm (Supplementary Table 3). For the 10 kb resolution data, the most important predictive features that were robust across cell lines were a mixture of transcription factor binding sites, chromatin states, and histone modifications including Smc3, Rad21, CTCF, and H3k9 trimethylation (Figure 6). [??? We don't care - these are for unbalanced dataset] Transcription factor binding sites Smc3, Rad21, and CTCF were also consitently featured as top predictors when comparing cell lines across the the 25 kb and 50 kb resolutions (Supplementary Figure 4). Results when cell lines were compared across the 100 kb resolutions were less consitent with current literature.
